Generating Images From Captions\\ With Attention

### 2015-11-01 iclr-paper-new.tex
u
a

\section{AlignDRAW Model}
\label{sec:model}
Our proposed model 
defines a generative process of images conditioned on captions. In particular, captions are represented as a sequence of consecutive words and images are represented as a sequence of patches drawn on a canvas $c_t$ over time $t=1,...,T$. The model can be viewed as a part of the sequence-to-sequence framework \citep{ilya_mt,cho_mt,nitish_video}.
%Our proposed model can be viewed as a part of sequence-to-sequence framework \citep{ilya_mt}, \citep{cho_mt}, \citep{nitish_video} where captions are represented as a sequence of consecutive words and images are represented as a sequence of patches drawn on canvas over time $t=1,...,T$. Let $\icaption$ be the input caption, consisting of $N$ words $y_{1}, y_{2}, ..., y_{n}$ and $\oimage$ be the image corresponding to that caption.

@@

\begin{figure}[t!]
\captionsetup[subfigure]{labelformat=empty}
\begin{center}
\includegraphics[width=0.99\textwidth]{figures/alignDrawAnnotated.pdf}\quad
%
\end{center}
\caption{The diagram shows our model learns to draw images by learning an alignment of input captions and generating canvas. The details are explained in Section \ref{sec:model}.}
\label{fig:figmodel}
\vspace{-0.3cm}
\end{figure}

@@

\subsection{Learning}
\label{sec:learning}
%The model is learned by the modified version of Stochastic Gradient Variation Bayes (SGVB) algorithm introduced by \cite{kingma_vae}. 
The model is trained to maximize a variational lower bound $\loss$ 
on the marginal likelihood of the correct image $\oimage$ given the input caption $\icaption$:
\beqa
\loss = \sum_{\Lat}Q(\Lat\given\oimage,\icaption)\bigg(\log P(\oimage\given\icaption, \Lat) - \kldiv\left(Q(\Lat\given\oimage,\icaption)\klBars 
  P(\Lat)\right)\bigg) \le \log P(\oimage\given\icaption).
\eeqa
%The posterior inference over the latent variables $\Lat_{1:T}$ is approximated using the inference RNN. 
Similar to the DRAW model, the inference recurrent network 
produces an approximate posterior $Q(\Lat_{1:T}\given\oimage,\icaption)$ via a $\readop$ operator, which reads a patch from image using two arrays of 1D Gaussian filters (inverse of $\writeop$ from section \ref{sec:image_model}), over the training image at each step. Specifically, 
\begin{align}
\label{eq:x_hat}
\hat{\oimage}_t &= \oimage-\sigmoid(\canv_{t-1}),\\
\label{eq:read}
r_t &= \readop(\oimage_t, \hat{\oimage}_t, \hdec_{t-1}),\\
\henc_t &= \encoder(\henc_{t-1}, [r_t, \hdec_{t-1}]),\\
\post(\Lat_t|\oimage,\icaption,\Lat_{1:t-1}) &= \mathcal{N}\left(\mu(\henc_t), \sigma(\henc_t)\right),
\end{align}
%The $\loss$ is decomposed into the latent loss $\lloss$ and the reconstruction loss $\rloss$. 
%The reconstruction loss $\rloss$ equals to $\frac{1}{L}\sum_{l=1}^{L}(log\,p(x_{t}|y,z)$ where $L$ is the number of samples used during training, which was set to $1$ in our experiments.
%The latent loss $\lloss$ is a negative sum of Kullback--Leibler divergence terms between distribution $\post(\Lat_t|\henc_t)$ and some prior distribution ${\prior(\Lat_t)}$ over time $t=1,...,T$, which can be seen as a regularization term. 
%Since the prior distribution at time $t$ is dependent on the sufficient statistics of the prior distribution at time $t-1$. Namely, the mean and variance of $\prior(\Lat_t)$ depends on the $\hdec_{t-1}$. 
%\begin{align}
%\mu_{t}^{prior} &= tanh(W_{\mu}\hdec_{t-1})\\
%\sigma_{t}^{prior} &= exp(tanh(W_{\sigma}\hdec_{t-1})) 
%\end{align}
where $\hat{\oimage}$ is the \textit{error} image and $\henc_0$ is initialized to the learned bias $b$. 
Note that the inference $\encoder$ 
takes as its input both the output
of the $\readop$ operator $r_t\in \real^{p\times p}$, which depends on the original input image $\oimage$,
and the previous state of the 
generative decoder $\hdec_{t-1}$, which depends on the latent sample history $z_{1:t-1}$ and 
dynamic sentence representation $s_t$ (see \Eqref{eq:decoder}). 
Hence, the approximate posterior $Q$ will depend on the input image $\oimage$,
the corresponding caption $\icaption$, and the latent history $\Lat_{1:t-1}$, except  
for the first step $Q(Z_1 | \oimage)$, which depends only on $\oimage$.

>>>>

\section{The AlignDRAW Model}
\label{sec:model}
Our proposed model 
defines a generative process of images conditioned on captions. In particular, captions are represented as a sequence of consecutive words and images are represented as a sequence of patches drawn on a canvas $c_t$ over time $t=1,...,T$. The model can be viewed as a part of the sequence-to-sequence framework \citep{ilya_mt,cho_mt,nitish_video}.
%Our proposed model can be viewed as a part of sequence-to-sequence framework \citep{ilya_mt}, \citep{cho_mt}, \citep{nitish_video} where captions are represented as a sequence of consecutive words and images are represented as a sequence of patches drawn on canvas over time $t=1,...,T$. Let $\icaption$ be the input caption, consisting of $N$ words $y_{1}, y_{2}, ..., y_{n}$ and $\oimage$ be the image corresponding to that caption.

@@

\begin{figure}[t!]
\captionsetup[subfigure]{labelformat=empty}
\begin{center}
\includegraphics[width=0.99\textwidth]{figures/alignDrawAnnotated.pdf}\quad
%
\end{center}
\caption{AlignDRAW model for generating images by learning an alignment between the input captions
and generating canvas. The caption is encoded using 
the Bidirectional RNN (left). The generative RNN takes a latent sequence $z_{1:T}$ sampled from the 
prior along with dynamic caption representation $s_{1:T}$ to generate the canvas matrix $c_T$, which is then
used to generate the final image $\oimage$ (right).
The inference RNN is used to compute approximate posterior $Q$ over the latent sequence.} 
\label{fig:figmodel}
\vspace{-0.3cm}
\end{figure}

@@

\subsection{Learning}
\label{sec:learning}
%The model is learned by the modified version of Stochastic Gradient Variation Bayes (SGVB) algorithm introduced by \cite{kingma_vae}. 
The model is trained to maximize a variational lower bound $\loss$ 
on the marginal likelihood of the correct image $\oimage$ given the input caption $\icaption$:
\beqa
\loss = \sum_{\Lat}Q(\Lat\given\oimage,\icaption) \log P(\oimage\given\icaption, \Lat) - \kldiv\left(Q(\Lat\given\oimage,\icaption)\klBars 
  P(\Lat \given\icaption)\right) \le \log P(\oimage\given\icaption).
\eeqa
%The posterior inference over the latent variables $\Lat_{1:T}$ is approximated using the inference RNN. 
Similar to the DRAW model, the inference recurrent network 
produces an approximate posterior $Q(\Lat_{1:T}\given\oimage,\icaption)$ via a $\readop$ operator, which reads a patch from image using two arrays of 1D Gaussian filters (inverse of $\writeop$ from section \ref{sec:image_model}), over the training image at each step. Specifically, 
\begin{align}
\label{eq:x_hat}
\hat{\oimage}_t &= \oimage-\sigmoid(\canv_{t-1}),\\
\label{eq:read}
r_t &= \readop(\oimage_t, \hat{\oimage}_t, \hdec_{t-1}),\\
\henc_t &= \encoder(\henc_{t-1}, [r_t, \hdec_{t-1}]),\\
\post(\Lat_t|\oimage,\icaption,\Lat_{1:t-1}) &= \mathcal{N}\left(\mu(\henc_t), \sigma(\henc_t)\right),
\end{align}
%The $\loss$ is decomposed into the latent loss $\lloss$ and the reconstruction loss $\rloss$. 
%The reconstruction loss $\rloss$ equals to $\frac{1}{L}\sum_{l=1}^{L}(log\,p(x_{t}|y,z)$ where $L$ is the number of samples used during training, which was set to $1$ in our experiments.
%The latent loss $\lloss$ is a negative sum of Kullback--Leibler divergence terms between distribution $\post(\Lat_t|\henc_t)$ and some prior distribution ${\prior(\Lat_t)}$ over time $t=1,...,T$, which can be seen as a regularization term. 
%Since the prior distribution at time $t$ is dependent on the sufficient statistics of the prior distribution at time $t-1$. Namely, the mean and variance of $\prior(\Lat_t)$ depends on the $\hdec_{t-1}$. 
%\begin{align}
%\mu_{t}^{prior} &= tanh(W_{\mu}\hdec_{t-1})\\
%\sigma_{t}^{prior} &= exp(tanh(W_{\sigma}\hdec_{t-1})) 
%\end{align}
where $\hat{\oimage}$ is the \textit{error} image and $\henc_0$ is initialized to the learned bias $b$. 
Note that the inference $\encoder$ 
takes as its input both the output
of the $\readop$ operator $r_t\in \real^{p\times p}$, which depends on the original input image $\oimage$,
and the previous state of the 
generative decoder $\hdec_{t-1}$, which depends on the latent sample history $z_{1:t-1}$ and 
dynamic sentence representation $s_t$ (see \Eqref{eq:decoder}). 
Hence, the approximate posterior $Q$ will depend on the input image $\oimage$,
the corresponding caption $\icaption$, and the latent history $\Lat_{1:t-1}$, except  
for the first step $Q(Z_1 | \oimage)$, which depends only on $\oimage$.
